\documentclass[9pt]{extarticle}

%------------------------Dimensions--------------------------------------------
\pagenumbering{gobble}
\topmargin=-20pt
\oddsidemargin=0.0in
\evensidemargin=0in
\textwidth=6.7in
\marginparwidth=0.5in
\headheight=0pt
\headsep=0pt
\textheight=9.5in

\usepackage{xcolor}
\definecolor{linkcolor}{RGB}{0,120,212}  % Microsoft blue (#0078D4)

\usepackage[utf8]{inputenc}
\usepackage[colorlinks=true,urlcolor=linkcolor,linkcolor=linkcolor]{hyperref}

\newcommand\tab[1][1cm]{\hspace*{#1}}
\newcommand\smallspace[1][0.23cm]{\hspace*{#1}}
\newcommand\negativespace[1][-0.12cm]{\hspace*{#1}}

% Arial setup
\usepackage[scaled]{helvet}
\renewcommand{\familydefault}{\sfdefault}

\begin{document}
	
\centerline{{\LARGE \bf Peter Sperl, B.Sc.}}
\centerline{\href{mailto:peter.sperl@outlook.com}{peter.sperl@outlook.com}}
\centerline{\href{https://github.com/leorean}{Github} \,|\, \href{https://www.linkedin.com/in/peter-sperl}{LinkedIn}}


\noindent %Prevents the following text from being indented
\\
\vspace*{-6pt}
{\negativespace \Large \bf Recent Professional Experience}\\
\line(1,0){485}\\
\vspace*{3pt}

{\bf Senior Engineer \& Team Lead}, \textit{\href{https://anyline.com}{Anyline}} \hfill \textit{2022 -- Present}
\begin{itemize}
	\setlength\itemsep{0.05em}
	\item Lead a cross-functional engineering team delivering high-performance scanning solutions across mobile, desktop (C\texttt{\#}), browser (C\texttt{++}/WebAssembly), and server (NestJS) platforms.
	\item Modernized the browser-based C\texttt{++} engine architecture, unifying the codebase and accelerating cross-platform feature delivery.
	\item Optimized CI/CD pipelines, reducing deployment times and increasing automated test coverage.
	\item Re-engineered the legacy C\texttt{++} monitoring module for improved stability, scalability, and maintainability.	
\end{itemize}

{\bf Senior Engineer}, \textit{\href{https://anyline.com}{Anyline}} \hfill \textit{2020 -- 2022}
\begin{itemize}
	\setlength\itemsep{0.05em}
	\item Designed and implemented a C\texttt{++} framework for platform-independent scanning — reducing internal development time by 60\% and standardizing capabilities across multiple platforms.
	\item Led the architecture overhaul of the UWP SDK, improving performance, robustness, and developer usability.
	\item Developed a \href{https://patents.google.com/patent/US20220327849A1/en}{patented over-the-air deployment system}, enabling closed-loop ML model updates in production.
	\item Architected \& enhanced SDK licensing module for improved security, stability and advanced feature control.
\end{itemize}

{\bf C\texttt{++} \& C\texttt{\#} Engineer}, \textit{\href{https://anyline.com}{Anyline}} \hfill \textit{2015 -- 2020}
\begin{itemize}
	\setlength\itemsep{0.05em}
	\item Ported TensorFlow to Windows x86/ARM architecture, enabling ML inference on embedded and mobile devices.
	\item Created the Anyline OCR Xamarin SDK for Android and iOS, powering real-time on-device text recognition.
	\item Ported the C\texttt{++} computer vision \& machine learning processing engine to Windows via C\texttt{++}/C\texttt{\#} bridge, enabling on-device OCR scanning on Windows-based devices.
	\item Developed a Unity-based HoloLens prototype for real-time recognition of serial numbers and utility meters in AR/MR environments.
	\item Developed, published and maintained \href{https://github.com/Anyline/anyline-ocr-examples-windows-uwp}{Anyline UWP SDK}.
	\item Designed \& optimized python-based image augmentation to provide datasets for training OCR models.
\end{itemize}
	
\noindent %Prevents the following text from being indented
\\
\\
\vspace*{-6pt}
{\negativespace \Large \bf Projects \& Developer Community Engagement}\\
\line(1,0){485}
\\
\\
\textbf{Game Development:} Developed multiple games \& projects using Unity, MonoGame, and Game Maker Studio.
\begin{itemize}
	\setlength\itemsep{0.05em}
	\item Developed a \href{https://github.com/leorean/GMStudio}{collection of 50+ Game Maker prototypes} exploring gameplay, AI, and rendering techniques.
	\item Created \href{https://github.com/leorean/SPG}{SPG}, an XNA-based SDK for rapid 2D game development.
	\item Level design for \href{https://ovos.at/de/projekte/cure-runners-ein-spiel-uber-geld-ohne-geld/}{Cure Runners}, a gamified learning experience.
\end{itemize}

\textbf{Hackathon Participation:} Active competitor in 15+ international coding competitions and game jams.
\begin{itemize}
	\setlength\itemsep{0.05em}
	\item \href{https://ldjam.com/events/ludum-dare/55/tao}{Tao} – placed 8th overall (out of 2000+) in Ludum Dare; made in LUA/pico8.
	\item \href{https://www.newgrounds.com/portal/view/599044}{Llama in Your Face} – browser game reaching 6M+ players globally.
	\item Additional submissions available \href{https://ldjam.com/users/leorean/games}{here}.
\end{itemize}
	
\noindent %Prevents the following text from being indented
\\
\vspace*{-6pt}
{\negativespace \Large \bf Education}\\
\line(1,0){485}\\
\\
\noindent
{\bf Bachelor of Science - Medical Informatics} \hfill \textit{2008 - 2013} \\
\textit{Technische Universität Wien} \\
\\
\\
{\bf Languages:} Modern C\texttt{++} (C\texttt{++17}/C\texttt{++20}), C\texttt{\# 12}, Python, Java, LUA, GML \\
{\bf Frameworks \& Tools:} TensorFlow, OpenCV, CMake, Conan, .NET 8, UWP, WPF, Unity, Xamarin, XNA, MonoGame, Game Maker Studio, GCP \\
{\bf Expertise:} Cross-platform C\texttt{++} development, performance optimization, real-time computer vision, SDK architecture, CI/CD automation, AR/VR prototyping
	
\end{document}
